Simulating High-Dimensional Multivariate Data

### 2021-02-25 050-examples.Rmd
changed object name

```{r ch050-lossResults, cache=FALSE}
frobenius_path <- paste0("results/brca_", d, "_frobenius.rds")
if (!file.exists(frobenius_path)) {
    N <- nrow(example_brca)
    ## create m random vectors and estimate correlation
    simRho <- replicate(n = m, expr = {
        tmpSim <- bs$rvec(N, R_X, nb_margins)
        bs$cor(tmpSim, bs$Spearman)
    }, simplify = FALSE)
    frobenius <- sapply(simRho, function(R) sum((R - R_S)^2))
    saveRDS(frobenius, frobenius_path)
}
frobenius_loss <- readRDS(frobenius_path)
```

>>>>

```{r ch050-lossResults, cache=FALSE}
frobenius_path <- paste0("results/brca_", d, "_frobenius.rds")
if (!file.exists(frobenius_path)) {
    N <- nrow(example_brca)
    ## create m random vectors and estimate correlation
    simRho <- replicate(n = m, expr = {
        tmpSim <- bs$rvec(N, R_X, nb_margins)
        bs$cor(tmpSim, bs$Spearman)
    }, simplify = FALSE)
    frobenius_loss <- sapply(simRho, function(R) sum((R - R_S)^2))
    saveRDS(frobenius_loss, frobenius_path)
}
frobenius_loss <- readRDS(frobenius_path)
```
